### 2016-03-23 config/styles.inc.tex
More uniform image styles

\colorlet{FSmooth}{TangoScarletRed3}
\colorlet{expFit}{TangoSkyBlue3}
\colorlet{trunc}{clogms}

@@

\pgfplotsset{histogramSmootherFTest/.style={ycomb,line width=1.5pt,fill=white!40!black,draw=white!40!black,area legend}}
\pgfplotsset{histogramSmootherExpFit/.style={ycomb,line width=1.5pt,fill=white!70!black,draw=white!70!black,opacity=0.8,area legend}}

>>>>

\colorlet{FSmooth}{TangoScarletRed3}
\colorlet{FSmoothLight}{TangoScarletRed2}
\colorlet{expFit}{TangoSkyBlue3}
\colorlet{expFitLight}{TangoSkyBlue2}
\colorlet{trunc}{clogms}

@@

% adapted from xbar legend from pgfplots manual
\pgfplotsset{logHistogramLegend/.style={/pgfplots/legend image code/.code={%
            \draw[##1,/tikz/.cd,bar width=3pt,yshift=-0.2em,bar shift=0pt]
            plot coordinates {(0.15cm,0.6em) (0.3cm,0.8em) (0.45cm,0.6em)};}
}}

\pgfplotsset{logHistogram/.style={ycomb,line width=1.5pt,logHistogramLegend}}
\pgfplotsset{histogramSmootherFTest/.style={logHistogram,fill=FSmoothLight,draw=FSmoothLight}}
\pgfplotsset{histogramSmootherExpFit/.style={logHistogram,fill=expFitLight,draw=expFitLight,opacity=0.8}}

\pgfplotsset{mainCurve/.style={color=black,solid,line width=1.5pt}}
\pgfplotsset{pointOfInterest/.style={color=black,mark size=1.5pt,only marks,mark=*,mark options={solid}}}
